---
title: "R with Regression and Visualization"
author: "Victoria Mosby"
date: '2022-12-07'
output:
  html_document:
    df_print: paged
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
class: Coding with R
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

## Prompt
Choose a different city from Vienna and make sure you have at least 100 observations after filtering.
Create at least 3 models with at least 3 explanatory variables (check for transformation) and choose the best. 
Imagine you can build a new hotel in your city and can specify the feature values as you wish. 
Predict the price and estimate confidence and prediction intervals with a 90% significance level.
Set the price of your hotel and argue, why is it your choice.

```{r}
library(tidyverse)
library(modelsummary)
library(fixest)
library(car)
if (!require(ggpubr)){
  if (!require(car)){
    install.packages('car')
  }
  install.packages('ggpubr')
  library(ggpubr)
}
library(lspline)
library(texreg)

#Clear the environment
rm(list=ls())
#####
# Import Data:
# now we use all the observations from Europe:
hotels_europe_price    <- read_csv('https://osf.io/p6tyr/download')
hotels_europe_features <- read_csv('https://osf.io/utwjs/download')

#Let's modify the dataset 
europe <- left_join(hotels_europe_price, hotels_europe_features, by = 'hotel_id')

#Originally I selected Athens but it had too few observations so I selected Barcelona which has 249
barcelona <- europe %>% filter(accommodation_type=='Hotel') %>%
  filter(year == 2017, month == 11, weekend == 0) %>% 
  filter(city_actual=='Barcelona') %>%
  filter(stars>=3 & stars<=4) %>% filter(!is.na(stars)) %>%
  filter(price<=600)

#Let's modify the dataset by changing the variable from price to log price
barcelona <- barcelona %>% mutate(lnprice = log(price))

#Let's remove Athens as it had too few observations 
rm(athens)

#Let's check the descriptive statistics here 
P95 <- function(x){ quantile(x,.95,na.rm=T)}
datasummary(price + lnprice + distance + stars + rating ~ 
              Mean + SD + Min + Max + Median + P95 + N, data = barcelona)

#Let's graph the data to get an idea of what the data can show
p1 <- ggplot(data = barcelona, aes(x = distance, y = lnprice)) +
  geom_point(color = 'red', size = 2, shape = 16,) + 
  geom_smooth(method = 'loess', formula = y ~ x) +
  labs(x = 'Distance to city center (miles)',y = 'Log of price (US dollars)')
p1

# p2: stars vs price
p2 <- ggplot(data = barcelona, aes(x = stars, y = lnprice)) +
  geom_point(color = 'green', size = 2, shape = 16,) + 
  geom_smooth(method = 'loess', formula = y ~ x) +
  labs(x = 'Star of the Hotel', y = 'Log of price (US dollars)')
p2
# Star of a hotel is discrete value: may use as it is, 

# Task: plot p3: rating vs price
p3 <- ggplot(data = barcelona, aes(x = rating, y = lnprice)) +
  geom_point(color = 'blue', size = 2, shape = 16,) + 
  geom_smooth(method = 'loess', formula = y ~ x) +
  labs(x = 'Ratings of the hotel',y = 'Log of price (US dollars)')
p3

#One method of combining the graphs is GGArrange, though I have used others in the past
plots <- ggarrange(p1, p2, p3,
                              hjust = -0.6,
                              ncol = 1, nrow = 3)
plots

barcelona1 <- na.omit(barcelona)

#Regression with rating
reg0 <- feols(lnprice ~ rating, data = barcelona1, vcov = 'hetero')
reg0

# Baseline B: use only distance with heteroscedastic SE
reg1 <- feols(lnprice ~ distance, data = barcelona1, vcov = 'hetero')
reg1

# Multiple regression with both rating and distance
reg2 <- feols(lnprice ~ distance + rating, data = barcelona1, vcov = 'hetero')
reg2


# More complex models: this is just to have here but I will not use it for evaluation as 
#I need to understand this better
reg3 <- feols(lnprice ~ lspline(distance, c(1,4)) + lspline(rating, 3.5) ,
              data = barcelona, vcov = 'hetero')
reg3

#The table from Gabors website 
etable(reg0, reg1, reg2)

#Let's use another method from a classmate who posted on slack to combine the regressions
screenreg(list(reg0,reg1,reg2), caption= "Regressions Results", caption.above=TRUE)
```
# Interpretation

Models 1 and 3 are highly significant (Model 2 is significant at the 10% level but the intercept shows it is not quite as accurate as the other models). However, model 3 is the most accurate having two explanatory variables that affect lnprice therefore, it is the best. 

```{r}
# Save the predicted and residual values
barcelona1$lnprice_hat   <- reg3$fitted.values
barcelona1$lnprice_resid <- reg3$residuals
# Note we are interested in real price values not in logs:
# the first term is straight forward, however the second exp(reg4$ssr /2) is a correction term 
#   which is needed when dealing with log to exp transformation. Later in DA3 it will be discussed.
corr_term <- exp(mean(barcelona1$lnprice_resid) / 2)
barcelona1$price_hat <- exp(barcelona1$lnprice_hat) * corr_term

#Top 5 Deals 
barcelona1 %>%  top_n(-5, lnprice_resid) %>% select(hotel_id, price, price_hat, lnprice, lnprice_hat ,
                                                lnprice_resid, distance, stars, rating)
# 1) y - yhat graph (regression line must be the same as the 45 degree line!)
ggplot(data = barcelona1, aes(x = lnprice_hat, y = lnprice)) +
  geom_point() + 
  geom_smooth(method='lm',formula=y~x,se=F) +
  labs(x = 'ln(predicted price, US dollars) ',y = 'ln(price, US dollars)')+
  geom_segment(aes(x = 5.1, y = 4.28, xend = 4.76, yend = 4.28), 
               arrow = arrow(length = unit(0.1, 'cm')),
               color = 'darkgreen')+
  annotate('text', x = 5.25, y = 4.29, label = 'Best deal', size=4,color = 'darkgreen')+
  geom_abline(intercept = 0, slope = 1, size = 0.5, color = 'red', linetype = 'dashed') +
  coord_cartesian(xlim = c(4, 5.5), ylim = c(4, 5.5)) +
  theme_bw()

ggplot(data = barcelona1, aes(x = lnprice_hat, y = lnprice_resid)) +
  geom_point(color = 'red', size = 2) + 
  geom_smooth(method='lm', colour='blue', se=F, formula = y~x) +
  labs(x = 'ln(Predicted hotel price, US dollars)',y = 'Residuals')+
  theme_bw() 

pred_CI <- predict(reg2, newdata = barcelona1, se.fit=T, interval = 'confidence')

# Add the CI values to barcelona dataset
barcelona1 <- barcelona1 %>% mutate(CI_up  = pred_CI$ci_high,
                            CI_low = pred_CI$ci_low)

new_hotel_barcelona <- tibble(distance = 2.5, star3 = 0, star35 = 0, rating = 3.2)
pred_CI_new <- predict(reg2, newdata = new_hotel_barcelona, se.fit=T, interval = 'confidence')
pred_CI_new

#predict the prediction interval
pred_PI <- predict(reg3, newdata = barcelona1, se.fit=T, interval = 'prediction', level=0.95)

# Check for our new hotel
pred_PI_new <- predict(reg3, newdata = new_hotel_barcelona, se.fit=T, interval = 'prediction', level=0.95)


pred_PI_new <- pred_PI_new %>% mutate(pred_price = exp(fit) * corr_term,
                                      PI_up = exp(ci_high)* corr_term,
                                      PI_low = exp(ci_low) * corr_term)
pred_PI_new

##Set the price of your hotel and argue, why is it your choice.

#Let us compare the two results for our newly predicted hotel:
new_hotel_price <- tibble(price = pred_CI_new$pred_price, 
                          CI_low = pred_CI_new$CI_low ,
                          CI_up = pred_CI_new$CI_up,
                          PI_low = pred_PI_new$PI_low ,
                          PI_up = pred_PI_new$PI_up)

# Results for the new price of hotels in Barcelona:
new_hotel_price
```

This price is good because at the 95% confidence interval, it gives a more accurate predicted value.We can compare this with other cities through RMSE analysis and compare the trend of the predicted value.
I have incorporated the new data in the actual dataset. Then used the following process.

```{r}
# we add a new row in our original data

barcelona2 <- add_row(barcelona1, hotel_id =1632, distance = 2.5, rating = 3.2, price =	
                        77.35838, lnprice= log(77.35838))

# Now we use our regression model 03 to predict the values of lnprice
pred_m1_test <- predict(reg3, newdata = barcelona2)


# Create a tibble to compare the results

pred_trend <- tibble(actual_lnprice = barcelona2$lnprice,
                     m1_lnprice = pred_m1_test)

# If you want to visualize

p4 <- ggplot(barcelona2) +
  geom_point(aes(x = lnprice, y = pred_m1_test), color = 'cyan1', size = 2) +
  geom_line(aes(x = lnprice, y = lnprice), color = 'navyblue', size = 1) +
  labs(x = 'Actual log price', y = 'Predicted log prices') +
  coord_cartesian(xlim = c(4, 5.5), ylim = c(4, 5.5)) +
  theme_bw()
p4
```

To visualize the whether the predicted trend best fit with the actual line.The new price is not an outlier. 

