---
title: "Hw 1 Coding 1"
author: "Victoria Mosby"
date: '2022-10-04'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Clear the environment


```{r}
rm(list = ls())

```

## Creating a string variable which states that this is my first assignment in R, but that is not true. This is however my first assignment in R Markdown.

```{r}
str_var = 'This is my first assignment in RMarkdown!'

```

#Checking to make sure that I have a string variable
``` {r}
typeof(str_var)
```

#Create a vector 'v', which contains: 3, 363, 777, 2021, -987 and Inf
```{r}
v = c(3, 363, 777, 2021, -987, Inf)

```

#Not part of the assignment but let's check to see what this is
```{r}
typeof(v)
```
#Now let's multiply this vector with 10 
```{r}
v_10 = v*10 
```
#Create a list, which contains str_var and v
```{r}
mL = list(str_var, v)
```
#Get the value of 'Inf' out of this 'mL' variable with indexing 
```{r}
typeof(mL[[2]][6])
```
#Decide whether the former extracted value is infinite or not. If false it is infinite
```{r}

is.finite(mL[[2]][6])
Inf == mL[[2]][6]
```

